### 2016-03-05 HSF-TN/draft-2016-VACPLAT/draft-HSF-TN-2016-VACPLAT.tex
Spell out cvmfs proxy pattern

>>>>

If the VM requires the address(es) of HTTP proxies to use with CernVM-FS,
it must expect this value as the special pattern 
\texttt{\#\#user\_data\_option\_cvmfs\_proxy\#\#} The VM must be able to
accept compound CernVM-FS proxy expressions containing semicolon and pipe 
characters. Typically this will involve placing the substitution pattern
in appropriate quotation marks within the user\_data template.
